---
title: "DPE_RTest"
author: "Reinp"
date: "`r Sys.Date()`"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
  word_document: default
---

# R Programming

## Set Chunk requirements

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

```


## 5. Import data into r

```{r}

library(tidyverse)
library(lubridate)
## tidyverse includes readr, ggplot2, dplyr, forcats, tibble, tidyr, purrr, stringr
library(stats)
library(readxl)



## Reading our dataset
setwd('F:/Documents/Reinp/GitHub Respositories/DPE_RTest')

R_test <- read_csv("R_test_dataset.csv")
View(R_test)

R_test <- R_test%>%
  mutate(Q_2 = dmy(Q_2))


```


### Structure of the data

```{r, include=FALSE}

head(R_test)

tail(R_test)

## How many variables and observations are there?
ncol(R_test)

nrow(R_test)

##learn more about the dataset
help(R_test)
??R_test


str(R_test)
class(R_test)
typeof(R_test) 
length(R_test) #number of variables
names(R_test) #display variable names

#attributes(R_test) names(R_test), class(R_test), row.names(R_test)

```


### Missing data

```{r}
#complete.cases(R_test) ##print logical vector indicating complete rows
                       ##(i.e. rows without NA)

#which(!complete.cases(R_test)) #print incomplete cases (rows with NA)

#R_test[complete.cases(R_test), ] ## Keep only the complete rows

#data_complete <- R_test[complete.cases(R_test), ] ## Store the complete cases subset in a new
                                                   ##data frame

#which(is.na(R_test)) #check for missing values

sum(is.na(R_test))

sapply(R_test,function(x) sum(is.na(x)))

```


## 6. Duplicated Cases

```{r}
#duplicated(R_test$SbjNum)
sum(duplicated(R_test$SbjNum))
table(duplicated(R_test$SbjNum))

#mean(duplicated(R_test$SbjNum)) #proportion of repeat cases

#sum(duplicated(R_test$SbjNum))/nrow(R_test)
```


## 7. total number of unique interviews 


```{r}

#unique(R_test$SbjNum)
#count(unique(R_test$SbjNum))
#table(unique(R_test$SbjNum))

## data with unique SbjNum

#R_testu <- R_test[!duplicated(R_test$SbjNum),]


R_testu <- R_test%>%
  filter(SbjNum == unique(SbjNum))


nrow(R_testu)
```


## 8. Assigning value labels to variables
```{r}

R_testu <- R_testu %>%
  mutate(Interviewer = if_else(Interviewer == 1, "Menya Abdmajid",
                        if_else(Interviewer == 2, "Bbale Denis",
                        if_else(Interviewer == 3, "Muwonge Allan Joshua",
                        if_else(Interviewer == 4, "Wambi Ken Paul",        
                        if_else(Interviewer == 5, "Wabwire Thomas", 
                        if_else(Interviewer == 6, "Muhindo Wilfred",
                        if_else(Interviewer == 7, "Ahumuza Owen",
                        if_else(Interviewer == 8, "Mirembe Mary",
                        if_else(Interviewer == 9, "Arinitwe Mackline",        
                        if_else(Interviewer == 10, "Alum Maria",
                        if_else(Interviewer == 11, "Kasule violet",        
                        if_else(Interviewer == 12, "Aweko Monica", "Nabbumba Pennina"       
                                )))))))))))))%>%
  mutate(S2 = if_else(S2 == 1, "17 and below",
                        if_else(S2 == 2, "18-25",
                        if_else(S2 == 3, "26-30", "31 and above" 
                                ))))%>%
  mutate(Social_Class = if_else(Social_Class == 1, "Social Class D",
                        if_else(Social_Class == 2, "Social Class C2",
                        if_else(Social_Class == 3, "Social Class C1", 
                         if_else(Social_Class == 4, "Social Class B", "Social Class A" 
                                )))))%>%
  mutate(B4 = if_else(B4 == 1, "Yes", "No"))%>%
  mutate(B17 = if_else(B17 == 1, "Extremely ready",
                        if_else(B17 == 2, "Somewhat ready",
                        if_else(B17 == 3, "Neutral", 
                         if_else(B17 == 4, "Not ready", "Definitely not ready" 
                                )))))%>%
  mutate(C1 = if_else(C1 == 1, "I have been employed",
              if_else(C1 == 2, "I am self-employed",
              if_else(C1 == 3, " unpaid intern", 
              if_else(C1 == 4, "household activities",
                      "I have not been employed" 
                                )))))


```


## 9. Number of Interviews conducted by each interviewer

```{r}

library(knitr)
#DollarSign Syntax

kable(table(R_testu$Interviewer))
```


## 10. Clean up the ward variable and then compute the number of interviews per ward 

```{r}

which(is.na(R_testu$Ward)) #check for missing values in ward

R_testu$Ward <- gsub("Bukoto Nsimbi ziwome", "Bukoto", R_testu$Ward)
R_testu$Ward <- gsub("Bukoto Nsimbi Ziwome", "Bukoto", R_testu$Ward)
R_testu$Ward <- gsub("Bukoto church", "Bukoto", R_testu$Ward)

R_testu$Ward <- gsub("KABOWA", "Kabowa", R_testu$Ward)
R_testu$Ward <- gsub("kabowa", "Kabowa", R_testu$Ward)
R_testu$Ward <- gsub("Kafumbe mukasa", "Kafumbe Mukasa", R_testu$Ward)
R_testu$Ward <- gsub("kagugube", "Kagugube", R_testu$Ward)
R_testu$Ward <- gsub("kamokya", "Kamwokya", R_testu$Ward)
R_testu$Ward <- gsub("KAMWOKYA", "Kamwokya", R_testu$Ward)
R_testu$Ward <- gsub("kansanga", "Kansanga", R_testu$Ward)
R_testu$Ward <- gsub("kasanga", "Kansanga", R_testu$Ward)
R_testu$Ward <- gsub("Kansanga kiwafu Estates", "Kansanga", R_testu$Ward)
R_testu$Ward <- gsub("kanyanya - komamboga zone A", "Kanyanya zone", R_testu$Ward)
R_testu$Ward <- gsub("kanyanya central zone 1", "Kanyanya zone", R_testu$Ward)
R_testu$Ward <- gsub("Kanyanya central zone B", "Kanyanya zone", R_testu$Ward)
R_testu$Ward <- gsub("kasubi", "Kasubi", R_testu$Ward)
R_testu$Ward <- gsub("KASUBI", "Kasubi", R_testu$Ward)
R_testu$Ward <- gsub("kawaala", "Kawaala", R_testu$Ward)
R_testu$Ward <- gsub("Kinawataka zone 1", "Kinawataka", R_testu$Ward)
R_testu$Ward <- gsub("KISASI DUNGU ZONE", "Dungu Zone", R_testu$Ward)
R_testu$Ward <- gsub("kisenyi", "Kisenyi", R_testu$Ward)
R_testu$Ward <- gsub("KISENYI", "Kisenyi", R_testu$Ward)
R_testu$Ward <- gsub("Kisenyi zone 3", "Kisenyi", R_testu$Ward)
R_testu$Ward <- gsub("kisira zone", "Kisira zone", R_testu$Ward)
R_testu$Ward <- gsub("kisugu", "Kisugu", R_testu$Ward)
R_testu$Ward <- gsub("Kisugu Upper Zone", "Kisugu", R_testu$Ward)
R_testu$Ward <- gsub("kiwatule", "Kiwatule", R_testu$Ward)
R_testu$Ward <- gsub("Kiwatule  kinyarwanda", "Kinyarwanda zone", R_testu$Ward)
R_testu$Ward <- gsub("Kiwatule kinyarwanda", "Kinyarwanda zone", R_testu$Ward)

R_testu$Ward <- gsub("lugala", "Lugala", R_testu$Ward)
R_testu$Ward <- gsub("Luwafu kirundu zone", "kiruddu", R_testu$Ward)

R_testu$Ward <- gsub("Makerere  University", "MAKERERE", R_testu$Ward)
R_testu$Ward <- gsub("Makerere Kagugube", "Kagugube", R_testu$Ward)
R_testu$Ward <- gsub("Makerere Kakugube", "Kagugube", R_testu$Ward)
R_testu$Ward <- gsub("makerere kakugube zone", "Kagugube", R_testu$Ward)
R_testu$Ward <- gsub("MAKERERE KAVULE", "Makerere kavule", R_testu$Ward)
R_testu$Ward <- gsub("Makerere kivulu", "Kivulu", R_testu$Ward)
R_testu$Ward <- gsub("Makerere Kivulu", "Kivulu", R_testu$Ward)
R_testu$Ward <- gsub("Mamerere Kagugube", "Kagugube", R_testu$Ward)
R_testu$Ward <- gsub("Makindyd Luwafu", "Makindye", R_testu$Ward)
R_testu$Ward <- gsub("makindye luwafu", "Makindye", R_testu$Ward)
R_testu$Ward <- gsub("Makindye luwafu", "Makindye", R_testu$Ward)
R_testu$Ward <- gsub("Makindye Luwafu", "Makindye", R_testu$Ward)
R_testu$Ward <- gsub("Makindye luwafu kirundu", "kiruddu", R_testu$Ward)
R_testu$Ward <- gsub("Makindye kirundu", "kiruddu", R_testu$Ward)
R_testu$Ward <- gsub("masanafu", "Masanafu", R_testu$Ward)
R_testu$Ward <- gsub("MASANAFU", "Masanafu", R_testu$Ward)
R_testu$Ward <- gsub("MBUYA", "Mbuya", R_testu$Ward)
R_testu$Ward <- gsub("Mbuya 1", "Mbuya", R_testu$Ward)
R_testu$Ward <- gsub("Mbuya kaggo", "Mbuya", R_testu$Ward)
R_testu$Ward <- gsub("Mbuya Kaggo", "Mbuya", R_testu$Ward)
R_testu$Ward <- gsub("Mbuya zone 1", "Mbuya", R_testu$Ward)
R_testu$Ward <- gsub("Mbuya kinawataka", "Kinawataka", R_testu$Ward)
R_testu$Ward <- gsub("Mulago ward C", "Mulago", R_testu$Ward)
R_testu$Ward <- gsub("Mutungo  Some 4", "Mutungo", R_testu$Ward)
R_testu$Ward <- gsub("Mutungo Biina", "Mutungo", R_testu$Ward)
R_testu$Ward <- gsub("Mutungo zone 4", "Mutungo", R_testu$Ward)
R_testu$Ward <- gsub("Mutungo Zone 4", "Mutungo", R_testu$Ward)
R_testu$Ward <- gsub("Mutungu", "Mutungo", R_testu$Ward)
R_testu$Ward <- gsub("Mutungo  Kampala road", "KAMPALA ROAD", R_testu$Ward)
R_testu$Ward <- gsub("Mutungo Kampala road", "KAMPALA ROAD", R_testu$Ward)

R_testu$Ward <- gsub("NABWERU ZONE 1", "Nabweru", R_testu$Ward)
R_testu$Ward <- gsub("nabweru zone1", "Nabweru", R_testu$Ward)
R_testu$Ward <- gsub("NAGURU BARRACKS", "NAGURU", R_testu$Ward)
R_testu$Ward <- gsub("NAKULABYE", "Nakulabye", R_testu$Ward)
R_testu$Ward <- gsub("NALUKABYE", "Nakulabye", R_testu$Ward)
R_testu$Ward <- gsub("NANKULABYE", "Nakulabye", R_testu$Ward)

R_testu$Ward <- gsub("NAMUNGONA", "Namungoona", R_testu$Ward)
R_testu$Ward <- gsub("Namungona Kisugu", "Namungoona", R_testu$Ward)
R_testu$Ward <- gsub("nsambya", "Nsambya", R_testu$Ward)
R_testu$Ward <- gsub("Nsambya  Barracks.", "Nsambya", R_testu$Ward)
R_testu$Ward <- gsub("Nsambya barracks", "Nsambya", R_testu$Ward)
R_testu$Ward <- gsub("Nsambya Barracks", "Nsambya", R_testu$Ward)
R_testu$Ward <- gsub("Nsambya kevina", "Nsambya", R_testu$Ward)
R_testu$Ward <- gsub("Nsambya Kevina", "Nsambya", R_testu$Ward)

R_testu$Ward <- gsub("Sebagala Zone", "Sebaggala zone", R_testu$Ward)
R_testu$Ward <- gsub("wandegeya.junju road", "Wandegeya", R_testu$Ward)
R_testu$Ward <- gsub("WANDEGEYA", "Wandegeya", R_testu$Ward)
R_testu$Ward <- gsub("wankulukuku", "Wankulukuku", R_testu$Ward)
R_testu$Ward <- gsub("WANKULUKUKU", "Wankulukuku", R_testu$Ward)
R_testu$Ward <- gsub("WUNKULUKUKU", "Wankulukuku", R_testu$Ward)

kable(table(R_testu$Ward))

```

## 11. interviews were conducted in every ward per interviewer 

```{r}

kable(table(R_testu$Ward, R_testu$Interviewer))

kable(table(R_testu$Interviewer, R_testu$Ward))

```


## 12.	Would you say older people are in high Social class?

```{r}


kable(table(R_testu$Social_Class, R_testu$A2))

kable(table(R_testu$A2, R_testu$Social_Class))

kable(table(R_testu$Social_Class, R_testu$S2))

kable(table(R_testu$S2, R_testu$Social_Class))

```


## 13.	What is the minimum, maximum, average and median age of the respondents 

```{r}
library(mosaic)
#favstats(~A2, data=R_testu)
kable(favstats(~A2, data=R_testu)[c("min", "max", "mean","median")])

#favstats(~B16, data=R_testu)
kable(favstats(~B16, data=R_testu)[c("min", "max", "mean","median")])

```

## 14.	Plot A2 against B16. Add title and axes labels 

### ggplot- lineplot

```{r}


ggplot(R_testu%>%group_by(A2) %>%summarise(B16 = mean(B16)), aes(A2, B16))+
  labs(title="Avearage amount willing to be paid for next degree/diploma", 
       x="Age of Respondents", y="Amount per Semester") +
  theme(axis.title=element_text(face="bold.italic", size="12", color="brown"), 
        axis.text = element_text(size = 8, face="bold"), 
        plot.title=element_text(size=12, face="bold", color="red", hjust = 0.5))+
  geom_point(size=2)+
  geom_line(colour="blue", size=1)+
  #geom_text(aes(label=R_testuplot$A2), nudge_x = 0.2, size=3)+
  scale_x_continuous(breaks = c(16, 18, 20, 22, 24, 26, 28, 30, 32), limits=c(17,31))+
  scale_y_continuous(breaks = c(0, 200000, 400000, 600000, 800000, 1000000, 1200000), 
                     limits=c(0,1200000))
  
#If the plot is on the screen ggsave(“path/filename.png”)

#If you have a plot object ggsave(myplot, file=“path/filename.png”)

#Specify size ggsave(myplot, “path/filename.png”, width=6, height=4)

# any plot format (pdf, png, eps, svg, jpg)


```

### ggplot Scatterplot


```{r}

ggplot(R_testu, aes(A2, B16))+
  labs(title="Amount willing to be paid for next degree/diploma", 
       x="Age of Respondents", y="Amount per Semester") +
  theme(axis.title=element_text(face="bold.italic", size="12", color="brown"), 
        axis.text = element_text(size = 8, face="bold"), 
        plot.title=element_text(size=12, face="bold", color="red", hjust = 0.5))+
  geom_point(size=2)+
  scale_x_continuous(breaks = c(16, 18, 20, 22, 24, 26, 28, 30, 32), limits=c(17,31))+
  scale_y_continuous(breaks = c(0, 250000, 500000, 750000, 1000000, 1250000, 1500000, 
                  1750000, 2000000, 2250000, 2500000, 2750000, 3000000, 3250000),
                  limits=c(0,3250000))

```

## 15.	What is the proportion of girls who are in non-girls only schools 


```{r}
#Was your school an all secondary girls school?
table(R_testu$B4)

prop.table(table(R_testu$B4))

```

## 16. dataset of the respondents who are aged between 18 – 25 years only 

```{r}
R_testu18_25 <- subset(R_testu, S2 == "18-25")

#write_excel_csv(R_testu18_25, "R_testu18_25.csv")

```


## 17.	Conduct any additional analysis in the data 

### Distribution of B16 Variable

```{r}

nrow(R_test)
nrow(R_testu)

R_testu1 = subset(R_testu, select = -c(Q_25_S,Q_32_S) ) #Delete column by name

R_testu1 <- na.omit(R_testu1) # Getting rid of missing data

nrow(R_testu1)

which(is.na(R_testu1)) #check for missing values
sum(is.na(R_testu1))

library(car)
library(MASS) #So that distributions that must be non-zero can make sense of my data


qqp(R_testu1$B16+1, "norm", main="Q-Q Plot ~ Normal model")

qqp(R_testu1$B16+1, "lnorm", main="Q-Q Plot ~ LogNormal model") #lnorm is lognormal

qqp(R_testu1$B16+1, "exp", main="Q-Q Plot ~ Exponential model")

#qqp requires estimates of the parameters of the negative binomial, Poisson
# and gamma distributions. You can generate estimates using the fitdistr function.
#negative binomial and gamma distributions can only handle positive numbers.
#Poisson distribution can only handle positive whole numbers.
#Binomial and Poisson distributions are different from the others because they are
#discrete rather than continuous, which means they quantify distinct,
#countable events or the probability of these events

nbinom <- fitdistr(R_testu$B16+1, "Negative Binomial")
qqp(R_testu$B16+1, "nbinom", size = nbinom$estimate[[1]], mu =
nbinom$estimate[[2]], main="Q-Q Plot ~ Negative Binomial model")

pois <- fitdistr(R_testu1$B16+1, "Poisson")
qqp(R_testu1$B16+1, "pois", lambda=pois$estimate, main="Q-Q Plot ~ Poisson model")

gamma <- fitdistr(R_testu1$B16+1, "gamma",
list(shape = 1, rate = 0.1), lower = 0.4)
qqp(R_testu1$B16+1, "gamma", shape = gamma$estimate[[1]], rate =
gamma$estimate[[2]], main="Q-Q Plot ~ Gamma model")

weibull <- fitdistr(R_testu1$B16+1, "weibull")
qqp(R_testu1$B16+1, "weibull", shape = weibull$estimate[[1]],
scale=weibull$estimate[[2]], main="Q-Q Plot ~ Weibull model")



```


### Multiple Regression

```{r}
#convert categorical variables to integer data types for regression purpose

R_testu_reg <- R_testu%>%
  mutate(S3 = if_else(S3 == 1, "None/did not complete",
              if_else(S3 == 2, "(UCE) 1-2 passes",
              if_else(S3 == 3, "(UCE) 3-5 passes",
              if_else(S3 == 4, "(UCE) 5 or more passes",        
              if_else(S3 == 5, "(UACE) – 1 principal", 
              if_else(S3 == 6, "(UACE) 2 principal", 
                    "(UACE) 3 principals")))))))%>%
  mutate(S4 = if_else(S4 == 1, "Yes", "No"))%>%
  mutate(S5_a = if_else(S5_a == 1, "Yes",
                        if_else(S5_a == 2, "No", "I don't know")))%>%
  mutate(A5 = if_else(A5 == 1, "Central",
              if_else(A5 == 2, "Western",
              if_else(A5 == 3, "Eastern",
              if_else(A5 == 4, "Northern", "Other")))))%>%
  mutate(A8 = if_else(A8 == 1, "Single",
              if_else(A8 == 2, "Married",
              if_else(A8 == 3, "Divorced or Separated", "Widowed"))))%>%
  mutate(A9 = if_else(A9 == 1, "I do not have children",
              if_else(A9 == 2, "I have 1 child",
              if_else(A9 == 3, "I have 2 children",
              if_else(A9 == 4, "I have 3 children", "I have more than 3 children")))))%>%
  mutate(A10 = if_else(A10 == 1, "I live alone",
              if_else(A10 == 2, "I live with one other person",
              if_else(A10 == 3, "I live with 2-3 other people",
              if_else(A10 == 4, "I live with 4-6 other people",
                      "I live with 7 or more people")))))%>%
  mutate(A12 = if_else(A12 == 1, "I am the head",
              if_else(A12 == 2, "I am the wife",
              if_else(A12 == 3, "I am the daughter",
              if_else(A12 == 4, "I am a relative",        
              if_else(A12 == 5, "I am a friend", 
              "Other"))))))%>%
  mutate(B8 = if_else(B8 == 1, "Diploma",
                        if_else(B8 == 2, "Technical certificate", "Bachelor's degree")))%>%
  mutate(S2 = factor(S2))%>%
  mutate(S3 = factor(S3))%>%
  mutate(S4 = factor(S4))%>%
  mutate(Social_Class = factor(Social_Class))%>%
  mutate(A5 = factor(A5))%>%
  mutate(A8 = factor(A8))%>%
  mutate(A9 = factor(A9))%>%
  mutate(A10 = factor(A10))%>%
  mutate(A12 = factor(A12))%>%
  mutate(B4 = factor(B4))%>%
  mutate(B8 = factor(B8))%>%
  mutate(B17 = factor(B17))%>%
  mutate(C1 = factor(C1))%>%
  dplyr:: rename(age_grouped = "S2",
                 secondary_school_certificate = "S3",
                 enrolled_tertiary_school_certificate = "S4",
                 age = "A2",
                 region_of_origin = "A5",
                 marital_status = "A8",
                 No_of_children = "A9",
                 No_people_living_with = "A10",
                 relationship_to_head_of_household = "A12",
                 all_secondary_girls_school = "B4",
                 career_next_level_of_education = "B8",
                 willing_to_pay_next_level_of_education = "B16",
                 career_ready = "B17",
                 employed_last_12months = "C1")%>%
dplyr:: select(7,10,13,14, 16,17, 18, 19, 22, 23, 24, 25, 26)%>%
  drop_na()

select

str(R_testu_reg)

```



```{r}
mlm1a <- lm(willing_to_pay_next_level_of_education ~ .,
data=R_testu_reg) #multiple regression
summary(mlm1a)
```


```{r}
# stepwise regression

library(MASS)
summary(stepAIC(mlm1a))


```


```{r}

R_testu_reg$predict_OLS <- round(predict(mlm1a, R_testu_reg),0)


sigma(mlm1a) #Residual Standard Error (RSE)


#accuracy of the model.
sigma(mlm1a)/mean(R_testu_reg$willing_to_pay_next_level_of_education) #The error rate

```

Error rate is high. (42.39%). count data is highly non-normal and is not well estimated by OLS regression.


Poisson regression is often used for modeling count data. (a type of data in which the observations can take only the non-negative integer values {0, 1, 2, 3, ... }, and where these integers arise from counting rather than ranking.)


### Poisson Regression


```{r}

mglm1a <-glm(formula = willing_to_pay_next_level_of_education ~ . -predict_OLS , data = R_testu_reg,
             family = poisson)
summary(mglm1a)


```

As over-dispersion is present in this data set, we re-compute the Wald tests using sandwich 
standard errors.

```{R}


library(sandwich)
library(lmtest)

coeftest(mglm1a, vcov = sandwich)

#coef(mglm1a, vcov = sandwich)


```



If the Residual Deviance is greater than the degrees of freedom, then over-dispersion exists. This means that the estimates are correct, but the standard errors (standard deviation) are wrong and unaccounted for by the model.

To have a more correct standard error we can use a quasi-poisson model. It uses the mean regression function and the variance function from the Poisson GLM but leaves the dispersion parameter unrestricted. Thus, dispersion parameter is not assumed to be fixed at 1 but is estimated from the data.

This leads to the same coefficient estimates as the standard Poisson model but inference is adjusted for over-dispersion.


### QuasiPoisson Regression

The model leads to an estimated dispersion parameter  which is clearly larger than 1, confirming that over-dispersion is present in the data.

```{r}

mglm1b <-glm(formula = willing_to_pay_next_level_of_education ~ . -predict_OLS , data = R_testu_reg,
             family = quasipoisson)
summary(mglm1b)

```

Since our count data is over-dispersed,( that is when the conditional variance exceeds the conditional mean), we can use negative binomial regression. It can be considered as a generalization of Poisson regression since it has the same mean structure as Poisson regression and it has an extra parameter to model the over-dispersion. If the conditional distribution of the outcome variable is over-dispersed, the confidence intervals for Negative binomial regression are likely to be narrower as compared to those from a Poisson regression.


### Negative binomial Model

If Theta is not known but to be estimated from the data, the negative binomial model is not a
special case of the general GLM—however, an ML fit can easily be computed re-using GLM
methodology by iterating estimation of Beta given Theta and vice versa. This leads to ML estimates
for both Beta and Theta which can be computed.

```{r}

mglm1c <-glm.nb(formula = willing_to_pay_next_level_of_education ~ . -predict_OLS , data = R_testu_reg)
summary(mglm1c)

```


```{r}

R_testu_reg$predict_NB <- round(predict(mglm1c, R_testu_reg, type = "response"),0)

```


Our count data does not have zero i.e zero cannot occur.

Ordinary Poisson regression and Ordinary Negative Binomial regression will have difficulty with zero-truncated data. It will try to predict zero counts even though there are no zero values.

The zero-truncated Poisson and negative binomial is designed for data that do not include zeroes. A sensible approach is to fit a Poisson or negative binomial model that excludes zero and rescales the other probabilities to sum to one. One should be careful interpreting these models because **mean** is not the expected outcome, but the mean of an underlying distribution that includes the zeros. These models are implemented in the vglm() function in the VGAM package, using the families pospoisson and posnegbinomial.


### Zero-truncated Poisson Model

Zero-truncated Poisson Regression is useful if you have no overdispersion. Since overdispersion is present in our data, we will model using Zero-truncated Negative binomial.


### Zero-truncated Negative binomial Model

```{r}

library(VGAM)

mglm1d <- vglm(formula = willing_to_pay_next_level_of_education ~ . -predict_OLS -predict_NB
               , family = posnegbinomial() ,data = R_testu_reg)

summary(mglm1d)

```

```{r}

R_testu_reg$predict_ZTNB <- round(predict(mglm1d, R_testu_reg, type = "response"),0)

```


### Comparison of the Count Models


Having fitted several count data regression models it is of interest to understand what these models have in common and what their differences are.


#### Estimates/Regression coefficients

1st comparison, we inspect the estimated regression coefficients in the count data models

```{R}

mglm1a_a <- coeftest(mglm1a, vcov = sandwich)

fm <- list( "Mult-OLS" = mlm1a , "Pois" = mglm1a, "Adj-Pois" = mglm1a_a,
            "Quasi-Pois" = mglm1b, "NegBin" = mglm1c, "ZT-NegBin" = mglm1d)

round(sapply(fm, function(x) coef(x)[1:36]), 4)


```

#### Standard Errors

2nd comparison the associated estimated standard errors

```{R}


round(cbind( "Mult-OLS" = sqrt(diag(vcov(mlm1a))), 
             "Pois" = sqrt(diag(vcov(mglm1a))), "Adj-Pois" = sqrt(diag(sandwich(mglm1a))),
      sapply(fm[-(1:3)], function(x) sqrt(diag(vcov(x)))[1:36])),4)

```

#### Log-Likelihood & AIC

3rd Comparison The differences of the models become obvious if not only the mean but the full likelihood is considered.

```{R}

rbind(logLik = sapply(fm, function(x) round(logLik(x), digits = 0)),
      Df = sapply(fm, function(x) attr(logLik(x), "df")),
      aic = sapply(fm, function(x) round(AIC(x), digits = 0)))

```

The Poisson model is clearly inferior to all other fits. The quasi-Poisson model is not associated with a fitted likelihood and Akaike's Information Criterion (AIC). 

The negative binomial already improves the fit dramatically but can in turn be improved by 
the zero inflated and hurdle model. 

The over-dispersion in the data is captured better by the negative-binomial-based models than 
the Poisson models.


#### df.residual, five-percent critical value of df.residual, deviance & Residuals Pearson's chi-squared

4th comparison

```{r}

rbind(df_residual = sapply(fm[-3], function(x) round(df.residual(x), digits = 0)),
      criticalvalue = sapply(fm[-3], function(x) round(qchisq(0.95, df.residual(x)), digits = 0)),
      dev = sapply(fm[-3], function(x) deviance(x)),
      resid.Pearson = sapply(fm[-3], function(x) round(sum((residuals(x,"pearson"))^2), 0))
      )

```


From the above comparisons, the negative binomial model is the best model to fit the data.






